{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-01-07 Notebook LaTEX/Proposal/main.tex
>w<, sync

                \item 

>>>>

                \item SVRG: Proximal stochastic gradient with progressive variance reduction. 
                \item Finito: A faster, permutable incremental gradient method for big data problems
                \item SAG: Minimizing finite sums with the stochastic average gradient
                \item SAGA: A fast increment al gradient method with support for non-strongly convex composite objectives. 

### 2025-01-07 Notebook LaTEX/R-WAPG/paper3.tex
>w<, sync

            Here is a list of papers that are relevant to generalizing the convergence claim for APG beyond just the traditional choices for the momentum sequence. 
                \item Attouch H., Cabot A.: ``Convergence Rates of Inertial Forward-Backward Algorithms'', SIAM. 
                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm beyond Nesterov's rule". 
            The following papers are related to stabilizing, improving the acceleration scheme without monotone restarting. 
                \item Attouch H., et al.: ``First-order optimization algorithms via inertial systems with Hessian driven damping'', Math Programming. 
            \textcolor{red}{The prior works' section is too little, it requires some expansion in the future for sure.} 

@@

    \subsection{Organizations}
        \todoinline{This will be written once most of the contents in the paper are settled. 
        }
        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize conditions for R-WAPG sequence sufficient to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}. 
        Section \ref{sec:rwapg-equiv-repr} gives 3 equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures. 
        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences and proves the convergence rate of several variants  FISTA using the R-WAPG algorithm and its convergence rate developed in the previous sections. 
        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcaes the numerical experiments for regression, LASSO, and logistic regression. 
        The numerical experiments exposes very interesting behaviors of the algorithm of our own creativity.

>>>>

            The prior works' section is too little, it requires some expansion in the future for sure.

@@

    \subsection{Organizations}
        \todoinline{This will be written once most of the contents in the paper are settled. 
        }
        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize conditions for R-WAPG sequence sufficient to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}. 
        Section \ref{sec:rwapg-equiv-repr} gives 3 equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures. 
        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences and proves the convergence rate of several variants  FISTA using the R-WAPG algorithm and its convergence rate developed in the previous sections. 
        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO, and logistic regression. 
        The numerical experiments expose very interesting behaviors of the algorithm of our own creativity.
